Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2019-01-07 tex/test-WW-type-01c.tex
new tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%

\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (c)}%
\includegraphics[height=3.5cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (d)}%
\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
	\cite{Schnell:2010zza}(c) in comparison to the best fit from \cite{Lefky:2014eia}
	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (d). For comparison the COMPASS plots
	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%

\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
